---
title: "STUDY OF CAMEROONIAN FIRMS' PERFORMANCE (Using panel data)"
output:
  word_document: default
  html_document: default
  pdf_document: default
editor_options: 
  markdown: 
    wrap: 72
---

This dissertation examines the performance of Cameroonian firms for data
collected in Cameroon over three periods: 2006, 2009, and 2016 by the
World Bank. The different stages of this work are:

-   General data base exploration
-   Database preparation
-   Descriptive Statistics
-   Stochastic frontier analysis
-   Stepwise elimination model
-   Selected model
-   Bivarial analysis of selected variables
-   Estimation
-   Use statistical tests to choose the best model

# Load data and useful librairies

```{r}
# Here we load useful libraries and data

library(tidyverse)
library(readxl)
library(ggplot2)
library(dplyr)
library(foreign)
library(plm)
#DATA <- Data
Data <- read_excel("D:/BEDIAM/CETIC/M2/MEMOIRE/Donnees+Documents_Prof/Bediam_Nonbo_Ebenezer/DATA.0.xlsx")

```

# General exploration of our data base.

```{r}
# Data size

dim(Data)
```

```{r}
#The most profitable activities in Cameroon in descending order

D22<-arrange(Data, desc(d22))   
D22<-select(D22, d1a1x, d22)
#View(D22)
head(D22)
```

```{r}
# Material inputs and suppliers of domestic origin in descending order

D12a <- arrange(Data,desc (d12a)) 
D12a  <- select( D12a,d1a1x,d12a)
head(D12a)
#view(D12a)
```

```{r}
# Material inputs and suppliers of foreign origin in descending order

D12b <- arrange(Data,desc (d12b)) 
D12b <- select( D12b,d1a1x,d12b)
head(D12b)
#view(D12a)
```

```{r}
# Example of companies not renting their premises

G6a <- arrange(Data,desc(g6a)) 
G6a <- select(G6a,d1a1x,g6a)
head(G6a)
```

```{r}
# Example of companies renting their premises

G6b <- arrange(Data,desc(g6b)) 
G6b <- select(G6b,d1a1x,g6b)
head(G6b)
```

We observe that only industrial production units with material inputs
and supplies of domestic origin build their infrastructures while
production units with material inputs and supplies of foreign origin
start on the basis of renting infrastructures.

# Database preparation

```{r}
# Here we select and rename useful variables

perform <- Data %>% select(panelid, year, a0,cap,d2, a3a, b7, b8, c22b, d1a3, d3a, d3c, d12a, d12b, e1, f1, f2, g6a, g6b, g5a, k3a, k3e, k3bc,
                           n5a, n5b, n2a,n2e,l1)
perform <- perform %>% rename(Panelid=panelid, Year=year,secteur=a0,capital=cap, vente_an=d2, region=a3a, Experience=b7, Certification=b8, Site_internet=c22b,
                              produit_principal=d1a3,
                              vente_nationale=d3a, export_direct=d3c, ressource_locale=d12a, ressource_exterieur=d12b,
                              marche_principal=e1, utilisation_ets=f1, Duree_travail=f2, construction_ets=g6a, local_loue=g6b,
                              espace_vente=g5a, capital_propre=k3a, capital_empr_NB=k3e, capital_empr_B=k3bc, Achat_equipement=n5a,
                              depense_construction=n5b, cout_travail=n2a, cout_materiel=n2e, emplyer_perm=l1)


## Transformation of categorical variables into factors

#perform$Year <- factor(perform$Year)
#perform$Panelid <- factor(perform$Panelid)
perform$region <- factor(perform$region)
perform$marche_principal <- factor(perform$marche_principal)
perform$Certification <- factor(perform$Certification)
perform$Site_internet <- factor(perform$Site_internet)

#perform$region <- recode_factor(perform$region, "1"="Littoral", "2"="Centre", "3"="West", "4"="Kribi")
```

```{r}
# Missing rate calculation

# loading library
library('dplyr')
#library('tidyverse')
# define the missing rate function

missing_rate <- function(df){
# calculate missing rate and transpose the DataFrame
rate <-t( df %>% summarize_all(funs(sum(is.na(.)) / length(.))))
# rename the column
colnames(rate)[1] <- "missing_rate"
print(rate)
}
#x
missing_rate(perform)

```

```{r}
# Transformation of data

perform$vente_an[perform$vente_an==0] <- 1
perform$lvente_an <- log(perform$vente_an)

perform$vente_nationale[perform$vente_nationale <= 69 ] <- 70
perform$vente_nationale[perform$vente_nationale == "" ] <- 80

perform$capital_empr_NB[perform$capital_empr_NB==0] <- 1
perform$lcapital_empr_NB <- log(perform$capital_empr_NB)

perform$capital[perform$capital==0] <- 1
perform$lcapital <- log(perform$capital)

perform$capital_empr_B[perform$capital_empr_B==0] <- 1
perform$lcapital_empr_B <- log(perform$capital_empr_B)

perform$capital_propre[perform$capital_propre==0] <- 1
perform$lcapital_propre <- log(perform$capital_propre)

perform$espace_vente[perform$espace_vente==0] <- 1
perform$lespace_vente <- log(perform$espace_vente)

perform$Achat_equipement[perform$Achat_equipement==0] <- 1
perform$lAchat_equipement <- log(perform$Achat_equipement)

perform$depense_construction[perform$depense_construction==0] <- 1
perform$ldepense_construction <- log(perform$depense_construction)

perform$cout_travail[perform$cout_travail==0] <- 1
perform$lcout_travail <- log(perform$cout_travail)

perform$cout_materiel[perform$cout_materiel<=0] <- 1
perform$lcout_materiel <- log(perform$cout_materiel)

perform$emplyer_perm[perform$emplyer_perm==0] <- 1
perform$lemplyer_perm <- log(perform$emplyer_perm)
```

# Descriptive Statistics

```{r}
## Missing values visualization

library(Amelia)
#Then, use the missmap function to plot the missing value map
missmap(perform, main="Missing Map before processing data")

```

```{r}
## Analysis of the Annual sales "vente_an"

#We will create visualizations to analyze vente_an. We will plot a histogram and then we will proceed to examine this data using a density plot
 
 summary(perform$vente_an)
 hist(perform$vente_an,
  col="#660033",
  main="Histogram for vente_an before transformation of data",
  xlab="vente_an Class",
  ylab="Frequency",
  labels=TRUE)

# plot(density(perform$vente_an),
#    col="yellow",
#    main="Density plot for vente_an before transformation of data",
#    xlab="vente_an Class",
#    ylab="Density")
 #polygon(density(perform$vente_an),
 #       col="#ccff66")

```

```{r}
## Analysis of the Annual vente_an

#We will create visualizations to analyze vente_an. We will plot a histogram and then we will proceed to examine this data using a density plot
 
 summary(perform$lvente_an)
 hist(perform$lvente_an,
  col="#660033",
  main="Histogram for lvente_an after transformation of data",
  xlab="lvente_an Class",
  ylab="Frequency",
  labels=TRUE)

# plot(density(perform$lvente_an),
#    col="yellow",
#    main="Density Plot for lvente_an after transformation data",
#    xlab="lvente_an Class",
#    ylab="Density")
# polygon(density(perform$lvente_an),
#        col="#ccff66")

```

```{r}
## Analysis of the Annual capital

#We will create visualizations to analyze capital We will plot a histogram and then we will proceed to examine this data using a density plot
 
 summary(perform$capital)
 hist(perform$capital,
  col="#660033",
  main="Histogram for capital before transformation of data",
  xlab="capital Class",
  ylab="Frequency",
  labels=TRUE)

 plot(density(perform$capital),
    col="yellow",
    main="Density Plot for capital before transformation of data",
    xlab="capital Class",
    ylab="Density")
 polygon(density(perform$capital ),
        col="#ccff66")

```

```{r}
## Analysis of the Annual capital

#We will create visualizations to analyze capital We will plot a histogram and then we will proceed to examine this data using a density plot
 
 summary(perform$lcapital)
 hist(perform$lcapital,
  col="#660033",
  main="Histogram for capital after transformation of data",
  xlab="lcapital Class",
  ylab="Frequency",
  labels=TRUE)

# plot(density(perform$lcapital),
#    col="yellow",
#    main="Density Plot for capital after transformation of data",
#    xlab="lcapital Class",
#    ylab="Density")
# polygon(density(perform$lcapital ),
#        col="#ccff66")
```

```{r}
## variable sector Visualization
#par(mfrow =c (1,2))
a=table(perform$secteur)
barplot(a,main="Comparison Viewer of sector variable",
       ylab="Count",
       xlab="secteur",
       col=rainbow(2),
       legend=rownames(a))
 
pct=round(a/sum(a)*100)
lbs=paste(c("Manufacturing","Other services","Retail services")," ",pct,"%",sep=" ")
library(plotrix)
pie3D(a,labels=lbs,main="Comparison Viewer of sector variable")
```

```{r}
## variable Certification Visualization
#par(mfrow =c (1,2))
a=table(perform$Certification)
barplot(a,main="Comparison Viewer of Certification variable",
       ylab="Count",
       xlab="Certification",
       col=rainbow(2),
       legend=rownames(a))
 
pct=round(a/sum(a)*100)
lbs=paste(c("1"="Yes","2"="No","3"="In process")," ",pct,"%",sep=" ")
library(plotrix)
pie3D(a,labels=lbs,main="Comparison Viewer of Certification variable")
```

```{r}
## variable website Visualization
#par(mfrow =c (1,2))
a=table(perform$Site_internet)
barplot(a,main="Comparison Viewer of website variable",
       ylab="Count",
       xlab="Site_internet",
       col=rainbow(2),
       legend=rownames(a))
 
pct=round(a/sum(a)*100)
lbs=paste(c("1"="Yes","2"="No")," ",pct,"%",sep=" ")
library(plotrix)
pie3D(a,labels=lbs,main="Comparison Viewer of website variable")
```

```{r}
## variable region Visualization
#par(mfrow =c (1,2))
a=table(perform$region)
barplot(a,main="Comparison Viewer of region variable",
       ylab="Count",
       xlab="region",
       col=rainbow(2),
       legend=rownames(a))
 
pct=round(a/sum(a)*100)
lbs=paste(c("1"="Littoral","2"="Centre","3"="West","4"="Kribi")," ",pct,"%",sep=" ")
library(plotrix)
pie3D(a,labels=lbs,main="Comparison Viewer of region variable")
```

```{r}
## variable marche_principal Visualization
#par(mfrow =c (1,2))
a=table(perform$marche_principal)
barplot(a,main="Comparison Viewer of main market variable",
       ylab="Count",
       xlab="marche_principale",
       col=rainbow(2),
       legend=rownames(a))
 
pct=round(a/sum(a)*100)
lbs=paste(c("1"="International","2"="National","3"="Local")," ",pct,"%",sep=" ")
library(plotrix)
pie3D(a,labels=lbs,main="Comparison Viewer of main market variable")
```

```{r}
library(ggplot2)

perform$marche_principal <-recode_factor(perform$marche_principal, "1"="International", "2"="National","3"="Local")
perform$Certification <- recode_factor(perform$Certification, "1"="Yes", "2"="No", "3"="In process")
perform$region <- recode_factor(perform$region, "1"="Littoral", "2"="Center", "3"="West","4"="Kribi")
perform$Site_internet <- recode_factor(perform$Site_internet, "1"="yes", "2"="No")
```

```{r}
#To examine more details about the relationship between the age and survival rate, one can use a boxplot

boxplot(perform$lvente_an ~ perform$Certification)
```

```{r}
#To examine more details about the relationship between the age and survival rate, one can use a boxplot

boxplot(perform$lvente_an ~ perform$region) 
```

```{r}
#To examine more details about the relationship between the age and survival rate, one can use a boxplot

boxplot(perform$lvente_an ~ perform$Site_internet) 
```

```{r}
#To examine more details about the relationship between the age and survival rate, one can use a boxplot

boxplot(perform$lvente_an ~ perform$marche_principal) 
```

```{r}

ggplot(data = perform, aes(x = marche_principal, y = lvente_an )) + 
    geom_boxplot(aes(fill = Certification)) + ggtitle("lvente_an ~ marche_principal") +
theme(legend.position = "bottom",
legend.title = element_text(face="bold"),
axis.title.x = element_text(face="italic"),
plot.title = element_text(colour = "purple",size = rel(1.5)))

```

```{r}
library(ggplot2)

ggplot(data = perform, aes(x = region, y = lvente_an )) + 
    geom_boxplot(aes(fill = Certification)) + ggtitle("lvente_an ~ region") +
theme(legend.position = "bottom",
legend.title = element_text(face="bold"),
axis.title.x = element_text(face="italic"),
plot.title = element_text(colour = "purple",size = rel(1.5)))

```

```{r}
library(ggplot2)

ggplot(data = perform, aes(x = Certification, y = lvente_an )) + 
    geom_boxplot(aes(fill = region)) + ggtitle("lvente_an ~ Certification") +
theme(legend.position = "bottom",
legend.title = element_text(face="bold"),
axis.title.x = element_text(face="italic"),
plot.title = element_text(colour = "purple",size = rel(1.5)))
```

```{r}
ggplot(data = perform, aes(x = region, y = lvente_an )) + 
    geom_boxplot(aes(fill = Certification)) + ggtitle("lvente_an ~ region") +
theme(legend.position = "bottom",
legend.title = element_text(face="bold"),
axis.title.x = element_text(face="italic"),
plot.title = element_text(colour = "purple",size = rel(1.5)))

```

```{r}
## summary of the data
summary(perform)
```

```{r}
## Standard deviation calculation
sd(perform$lvente_an)
sd(perform$Experience,na.rm = TRUE)
sd(perform$produit_principal,na.rm = TRUE)
sd(perform$vente_nationale,na.rm = TRUE)
sd(perform$export_direct,na.rm = TRUE)
sd(perform$ressource_locale,na.rm = TRUE)
sd(perform$ressource_exterieur,na.rm = TRUE)
sd(perform$utilisation_ets,na.rm = TRUE)
sd(perform$Duree_travail,na.rm = TRUE)
sd(perform$construction_ets,na.rm = TRUE)
sd(perform$local_loue,na.rm = TRUE)
sd(perform$lespace_vente,na.rm = TRUE)
sd(perform$lcapital,na.rm = TRUE)
sd(perform$lcapital_propre,na.rm = TRUE)
sd(perform$lcapital_empr_NB,na.rm = TRUE)
sd(perform$lcapital_empr_B,na.rm = TRUE)
sd(perform$lAchat_equipement,na.rm = TRUE)
sd(perform$ldepense_construction,na.rm = TRUE)
sd(perform$lcout_travail,na.rm = TRUE)
sd(perform$lcout_materiel,na.rm = TRUE)
sd(perform$lemplyer_perm,na.rm = TRUE)
```

```{r}
## Descriptive statistics of qualitative variables
table(perform$region)
table(perform$region) / nrow(perform)

table(perform$Certification)
table(perform$Certification) / nrow(perform)

table(perform$Site_internet)
table(perform$Site_internet) / nrow(perform)

table(perform$marche_principal)
table(perform$marche_principal) / nrow(perform)

```

# Stochastic frontier analysis

```{r}
## Filter data according to business sectors
perform_1M =perform[perform$secteur == "Manufacturing",]
perform_1O =perform[perform$secteur == "Other services",]
perform_1R =perform[perform$secteur == "Retail services",]


```

```{r}
## Code of stochastic frontier estimation (general model)
library( "plm" )
library(frontier)

riceTimeInv <- pdata.frame( perform, c( "Panelid", "Year" ) )
# Error Components Frontier (Battese & Coelli 1992)
# with time-invariant efficiencies
riceTimeInv <- sfa( log( vente_an ) ~ log( emplyer_perm ) + log( capital ) + log(Achat_equipement ),
data = perform )
summary( riceTimeInv )

```

```{r}
# Add data set with information about its panel structure

library( "plm" )
library(frontier)

riceTimeInvO <- pdata.frame( perform_1O, c( "Panelid", "Year" ) )
# Error Components Frontier (Battese & Coelli 1992)
# with time-invariant efficiencies
riceTimeInvO <- sfa( log( vente_an ) ~ log( emplyer_perm ) + log( capital ) + log(Achat_equipement ),
data = perform_1O )
summary( riceTimeInvO )

```

```{r}
# Add data set with information about its panel structure

library( "plm" )
library(frontier)

riceTimeInvR <- pdata.frame( perform_1R, c( "Panelid", "Year" ) )
# Error Components Frontier (Battese & Coelli 1992)
# with time-invariant efficiencies
riceTimeInvR <- sfa( log( vente_an ) ~ log( emplyer_perm ) + log( capital ) + log(Achat_equipement ),
data = perform_1R )
summary( riceTimeInvR )

```

```{r}
# Add data set with information about its panel structure

library( "plm" )
library(frontier)

riceTimeInvM <- pdata.frame( perform_1M, c( "Panelid", "Year" ) )
# Error Components Frontier (Battese & Coelli 1992)
# with time-invariant efficiencies
riceTimeInvM <- sfa( log( vente_an ) ~ log( emplyer_perm ) + log( capital ) + log(Achat_equipement ),
data = perform_1M )
summary( riceTimeInvM )

```

# Stepwise Selection model

```{r}
## Code of stepwise selection model
library(olsrr)
model<- lm(lvente_an~region+Certification+produit_principal+vente_nationale+ressource_locale+marche_principal+utilisation_ets+construction_ets+lcapital+lcapital_propre+lcapital_empr_B+lAchat_equipement+lemplyer_perm+lcout_travail+lcout_materiel+ldepense_construction+lcapital_empr_NB+Duree_travail+ressource_exterieur+export_direct+Site_internet ,data=perform)
Bothfit.p<-ols_step_both_p(model,pent=0.05,prem =.05)
Bothfit.p
```

# Selected model

Following the previous result, the selected model is the following:

lvente_an
\~lcapital+lcout_travail+lemplyer_perm+lcout_materiel+lAchat_equipement+Certification+region+marche_principal+Site_internet

## Bivarial analysis of selected variables

```{r}
## Correlation matrix of selected variables
MV <- subset(perform, select=c(lvente_an,lcapital,lcout_travail,lemplyer_perm ,lAchat_equipement,lcout_materiel))
mcor  <- cor(MV, use = "complete.obs")
mcor

```

```{r}
## Correlation matrix plot
library(corrplot)
corrplot(mcor, type="upper", order="hclust", tl.col="black", tl.srt=45)

```

```{r}

qplot(lcapital , lvente_an, data=perform)+ aes(colour = Certification) + ggtitle("Sales based on capital") +
theme(legend.position = "bottom",
legend.title = element_text(face="bold"),
axis.title.x = element_text(face="italic"),
plot.title = element_text(colour = "purple",size = rel(1.5)))
```

```{r}
qplot(lcapital , lvente_an, data=perform)+ aes(colour = region) + ggtitle("Sales based on capital") +
theme(legend.position = "bottom",
legend.title = element_text(face="bold"),
axis.title.x = element_text(face="italic"),
plot.title = element_text(colour = "purple",size = rel(1.5)))
```

```{r}
qplot(lemplyer_perm , lvente_an, data=perform)+ aes(colour = region) + ggtitle("lvente_an ~ lemplyer_perm") +
theme(legend.position = "bottom",
legend.title = element_text(face="bold"),
axis.title.x = element_text(face="italic"),
plot.title = element_text(colour = "purple",size = rel(1.5)))

```

```{r}
qplot(lcout_materiel , lvente_an, data=perform)+ aes(colour = Certification) + ggtitle("Sales based on size") +
theme(legend.position = "bottom",
legend.title = element_text(face="bold"),
axis.title.x = element_text(face="italic"),
plot.title = element_text(colour = "purple",size = rel(1.5)))

```

```{r}
qplot(lAchat_equipement , lvente_an, data=perform)+ aes(colour = Certification) + ggtitle("Sales based on the purchase of equipment") +
theme(legend.position = "bottom",
legend.title = element_text(face="bold"),
axis.title.x = element_text(face="italic"),
plot.title = element_text(colour = "purple",size = rel(1.5)))

```

```{r}
qplot(lAchat_equipement , lvente_an, data=perform)+ aes(colour = region) + ggtitle("Sales based on the purchase of equipment") +
theme(legend.position = "bottom",
legend.title = element_text(face="bold"),
axis.title.x = element_text(face="italic"),
plot.title = element_text(colour = "purple",size = rel(1.5)))

```

```{r}
qplot(region , lvente_an, data=perform)+ aes(colour = Certification) + ggtitle("lvente_an ~ region") +
theme(legend.position = "bottom",
legend.title = element_text(face="bold"),
axis.title.x = element_text(face="italic"),
plot.title = element_text(colour = "purple",size = rel(1.5)))

```

```{r}
## In addition to oneway.test, a standard function, aov, is used for the ANOVA analysis
 FEc.aov = aov(perform$lvente_an ~ perform$Certification)
 summary(FEc.aov)
 

```

```{r}
 FEc_posthoc =TukeyHSD(FEc.aov)
 FEc_posthoc
#Further, we can visualize the differences in mean level with a plot function:
 plot( FEc_posthoc)
 

```

```{r}
## In addition to oneway.test, a standard function, aov, is used for the ANOVA analysis:

 FEr.aov = aov(perform$lvente_an ~ perform$region)
 summary(FEr.aov)
 
```

```{r}
 FEr_posthoc =TukeyHSD(FEr.aov)
 FEr_posthoc
#Further, we can visualize the differences in mean level with a plot function:
 plot( FEr_posthoc)

```

```{r}
## Next, we use an interaction plot to characterize the relationship between variables:

interaction.plot(perform$region, perform$Certification, perform$lvente_an, type="b",col=c(1:3),leg.bty="o", leg.bg="beige", lwd=2, pch=c(18,24,22), xlab="region", ylab="lvente_an", main="Interaction Plot")

```

```{r}
##  We then perform a two-way ANOVA on perform_1 with a combination of the region and certification factors:
 mpg_anova2 = aov(perform$lvente_an~(perform$region)*(perform$Certification))
 summary(mpg_anova2)

```

# Estimation

```{r}
## Test homoscedasticity in panel data using R-studio
# Packages~ lmtest,plm
#Step1: pdata=pdata.frame(datafilename,index=C("firm","year"))
#Step2: bptest(invest~value+capital,data=pdata,studentize=F)  bptest:Breusch pagan test
#H0: There is homoscedasticity
#p-value is less than 5%
library(lmtest)
library(plm)
bptest(lvente_an ~lcapital+lcout_travail+lemplyer_perm+lcout_materiel+lAchat_equipement+Certification+region+marche_principal+Site_internet,data=perform,studentize=F)

# Conclusion: (p-value < 0.05) There is heteroscedasticity
```

```{r}
## Test for individual and time effect for Panel data:
# Model: Yit = u + bXit + ai + vt + uit ; ai = 0: 
#individual effect, vt = 0: time effect
plmtest(lvente_an ~lcapital+lcout_travail+lemplyer_perm+lcout_materiel+lAchat_equipement+Certification+region+marche_principal+Site_internet,data=perform,effect = "twoways",type = "ghm")
# H0: No significant individual and time effects
# H1: significant individual and time effects

# Conclusion: (p-value > 0.05) No significant individual and time effects
```

```{r}
## Test for individual and time effect for Panel data
# Model: Yit = u + bXit + ai + vt + uit ; ai = 0: 
#individual effect, vt = 0: time effect
plmtest(lvente_an ~lcapital+lcout_travail+lemplyer_perm+lcout_materiel+lAchat_equipement+Certification+region+marche_principal+Site_internet,data=perform,effect = "time",type = "kw")
# H0: No significant individual and time effects
# H1: significant individual and time effects

# Conclusion: (p-value > 0.05) No significant individual and time effects
```

```{r}
# Model: Yit = u + bXit + ai + vt + uit ; ai = 0: 
#individual effect, vt = 0: time effect
plmtest(lvente_an ~lcapital+lcout_travail+lemplyer_perm+lcout_materiel+lAchat_equipement+Certification+region+marche_principal+Site_internet,data=perform,effect = "individual",type = "kw")
# H0: No significant individual and time effects
# H1: significant individual and time effects

# Conclusion: (p-value > 0.05) No significant individual and time effects
```

```{r}
## Heterogeineity across Companies
library(foreign)
library(gplots)
library(plm)
pdata=pdata.frame(perform,index=c("Panelid","Year"))

plotmeans(lvente_an ~ Panelid, main="Heterogeineity across Companies", data=pdata)

```

```{r}
## Heterogeineity across Year
plotmeans(lvente_an ~ Year, main="Heterogeineity across Year", data=pdata)

```

```{r}
## LSDV estimation
library(foreign)
fixed.dum <-lm(lvente_an ~ lcapital+lcout_travail+lemplyer_perm+lcout_materiel+lAchat_equipement+Certification+region+marche_principal+Site_internet + factor(Panelid) - 1, data=pdata)
summary(fixed.dum)

```

```{r}
## LSDV estimation
library(foreign)
fixed.dumy <-lm(lvente_an ~ lcapital+lcout_travail+lemplyer_perm+lcout_materiel+lAchat_equipement+Certification+region+marche_principal+Site_internet + factor(Year) - 1, data=pdata)
summary(fixed.dumy)

```

```{r}
## Between effect method
library(plm)
pdata=pdata.frame(perform,index=c("Panelid","Year"))

betmethod=plm(lvente_an ~lcapital+lcout_travail+lemplyer_perm+lcout_materiel+lAchat_equipement+Certification+region+marche_principal+Site_internet,data = pdata,model  = "between")
summary(betmethod)
```

```{r}
## Fixed effect method
library(plm)
pdata=pdata.frame(perform,index=c("Panelid","Year"))

femethod=plm(lvente_an ~lcapital+lcout_travail+lemplyer_perm+lcout_materiel+lAchat_equipement+Certification+region+marche_principal+Site_internet,data = pdata,model  = "within")
summary(femethod)
```

```{r}
## Fixed effect method residual histogram
hist(resid(femethod), col = "grey",main="")

```

```{r}
## Random effect method
library(plm)
pdata=pdata.frame(perform,index=c("Panelid","Year"))

remethod=plm(lvente_an ~lcapital+lcout_travail+lemplyer_perm+lcout_materiel+lAchat_equipement+Certification+region+marche_principal+Site_internet, data = pdata, model = "random")

summary(remethod)
```

```{r}
## Fixed effect method residual histogram
hist(resid(remethod), col = "grey",main="")

```

# Use statistical test(s) to choose the best model

```{r}
## Hausman test which is usefull to choose between fixed effect model and random effect model
#Step1:Store the outcome of fixed effect model
#Step2:Store the outcome of random effect model
#Step3: phtest(fixed effect model,random effect model)
#H0:Random effect model is consistent
#H1:fixed effect model is consistent
library(plm)
phtest(femethod,remethod)   #Here we use p-value to choose

# Conclusion: (p-value < 0.05)fixed effect model is consistent
```
